Morphological Operations Applied to Digital Art Restoration

### 2014-04-10 LaTeX Paper/paper.tex
Added reference to Gaussian filter section.

In order to fulfill these criteria, the Canny algorithm first uses a Gaussian filter to smooth the image. This is achieved by passing the filter over each pixel in turn, blending each into the surrounding pixels. The complete result is a slightly blurred version of the original image with no isolated, ``noisy'' pixels (pixels that exhibit a significant jump in intensity from all surrounding pixels).

>>>>

In order to fulfill these criteria, the Canny algorithm first uses a Gaussian filter to smooth the image. This is achieved by passing the filter over each pixel in turn, blending each into the surrounding pixels. The complete result is a slightly blurred version of the original image with no isolated, ``noisy'' pixels (pixels that exhibit a significant jump in intensity from all surrounding pixels)~\cite{Canny:1986, CannySummarized}.
